\input{introduction}
\input{material}
\input{methods}

\newpage
\input{results}

\clearpage
\newpage
\input{discussions}
\input{conclusions}


\newpage\clearpage
\bibliographystyle{abbrvnat}
\bibliography{references.bib}

\clearpage
\newpage

\section*{Tables}

\begin{table}[ht]
\label{tab:grid}
\caption{Operating Model Scenarios; Base Case values in bold.}  
\begin{center}
\label{tab:datasumm}
\small

\begin{tabular}{|lccc|}

\hline
Factor & {Levels (N)} & {$\prod$ N} & {Values} \\ %& {Prior} & {Weighting}\\
\hline\hline
{Natural mortality (M)& {5}}  & {  5}  & { 0202  \textbf{0303} 0404 0403 0402}    \\
{Steepness of the stock-recruitment relationship}}& {3} 	 & {15}  & { \textbf{.7}; 0.8; 0.9} \\
{Variability of recruitment (sigmaR)}& {2} 	 & { 30}  & { \textbf{0.4}; 0.6} \\
{Effective Sampling Size of the length composition data (ESS)}& {3} & { 90}  & { 20; \textbf{50}; 100} \\
{CV for fit to CPUE (cpuecv)}& {4} 	 & { 360}  & { 0.2;  \textbf{0.3}; 0.4; 0.5} \\
{Yearly increase in catchability coefficient of CPUE (llq)}& {2} 	 & {  720}  & { \textbf{0\%}; 0.25\%} \\
  {Selectivity (llsel)}& {2}}& {1440}} & { \textbf{logistic} double normal} \\
\hline

\end{tabular}
\end{center}
\end{table}

\newpage
\input{figures}

\end{document}

\clearpage
\newpage
\section{Tables}

\begin{table}[!ht]
\label{tab:grid}
\caption{Operating Model Scenarios; Base Case values in bold.}  
\begin{center}
\label{tab:datasumm}
\begin{tabular}{|lccc|}
\hline
& {\tiny Levels (N)} & {\tiny $\prod$ N} & {\tiny Values} \\ %& {\tiny Prior} & {\tiny Weighting}\\
\hline\hline
{\tiny Natural mortality (M)& {\tiny 5}}  & {\tiny   5}  & {\tiny  0202  \textbf{0303} 0404 0403 0402}    \\
{\tiny Steepness of the stock-recruitment relationship}}& {\tiny 3} 	 & {\tiny 15}  & {\tiny  \textbf{.7}; 0.8; 0.9} \\
{\tiny Variability of recruitment (sigmaR)}& {\tiny 2} 	 & {\tiny  30}  & {\tiny  \textbf{0.4}; 0.6} \\
{\tiny Effective Sampling Size of the length composition data (ESS)}& {\tiny 3} & {\tiny  90}  & {\tiny  20; \textbf{50}; 100} \\
{\tiny CV for fit to CPUE (cpuecv)}& {\tiny 2} 	 & {\tiny  360}  & {\tiny  0.2;  \textbf{0.3}; 0.4; 0.5} \\
{\tiny Yearly increase in catchability coefficient of CPUE (llq)}& {\tiny 2} 	 & {\tiny   720}  & {\tiny  \textbf{0\%}; 0.25\%} \\
{\tiny Selectivity (llsel)}& {\tiny 2}}& {\tiny 1440}} & {\tiny  \textbf{logistic} double normal} \\
\hline

\end{tabular}
\end{center}
\end{table}

\begin{table}[!ht]
\caption{Mohn's $\rho$ for retrospective analysis.}  
\label{tab:retro}
\centering
\begin{tabular}{rllr}
  \hline
 & run & variable & $\rho$ \\ 
  \hline
  1 & ... & stock & ... \\ 
   \hline
\end{tabular}
\end{table}


\end{document}

\subsection{How to include Figures}

First you have to upload the image file from your computer using the upload link the project menu. Then use the includegraphics command to include it in your document. Use the figure environment and the caption command to add a number and a caption to your figure. See the code for Figure \ref{fig:frog} in this section for an example.

\subsection{How to add Comments}

Comments can be added to your project by clicking on the comment icon in the toolbar above. % * <john.hammersley@gmail.com> 2016-07-03T09:54:16.211Z:
%
% Here's an example comment!
%
To reply to a comment, simply click the reply button in the lower right corner of the comment, and you can close them when you're done.

Comments can also be added to the margins of the compiled PDF using the todo command\todo{Here's a comment in the margin!}, as shown in the example on the right. You can also add inline comments:

\todo[inline, color=green!40]{This is an inline comment.}

\subsection{How to add Tables}

Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example. 

\begin{table}
\centering
\begin{tabular}{l|r}
Item & Quantity \\\hline
Widgets & 42 \\
Gadgets & 13
\end{tabular}
\caption{\label{tab:widgets}An example table.}
\end{table}

\subsection{How to write Mathematics}

\LaTeX{} is great at typesetting mathematics. Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
\[S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i\]
denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.


\subsection{How to create Sections and Subsections}

Use section and subsections to organize your document. Simply use the section and subsection buttons in the toolbar to create them, and we'll handle all the formatting and numbering automatically.

\subsection{How to add Lists}

You can make lists with automatic numbering \dots

\begin{enumerate}
\item Like this,
\item and like this.
\end{enumerate}
\dots or bullet points \dots
\begin{itemize}
\item Like this,
\item and like this.
\end{itemize}

\subsection{How to add Citations and a References List}

You can upload a \verb|.bib| file containing your BibTeX entries, created with JabRef; or import your \href{https://www.overleaf.com/blog/184}{Mendeley}, CiteULike or Zotero library as a \verb|.bib| file. You can then cite entries from it, like this: \cite{greenwade93}. Just remember to specify a bibliography style, as well as the filename of the \verb|.bib|.

You can find a \href{https://www.overleaf.com/help/97-how-to-include-a-bibliography-using-bibtex}{video tutorial here} to learn more about BibTeX.

We hope you find Overleaf useful, and please let us know if you have any feedback using the help menu above --- or use the contact form at \url{https://www.overleaf.com/contact}!
